Reviving the Lost Art of \\Combinator Graph Reduction

### 2023-01-28 experiments/superg/doc/paper/paper.tex
Add intro to perf. eval.

\subsection{Comparison with original Miranda}
Figure~\ref{fig:turner-vs-miranda} shows the performance of our Miranda-style engine with the traditional bracket abstraction compared to the original Miranda~\cite{turner_open_2021}.
The test program used for the benchmark is the function given in Figure~\ref{fig:fib}.

@@

>>>>

The program used in these benchmarks is a recursive definition of a function to compute elements of the Fibonacci sequence.
Figure~\ref{fig:fib} shows the definition of the function in the Miranda language (for use with the original Miranda), as well as a definition in the LISP-like language used by our tools.
The two definitions are identical, all differences are syntactical.
In our benchmarks, we vary the value of parameter $n$ between $10$ and $20$ to show how the execution time changes as we increase the number of recursive calls (and therefore the number of operations performed).

@@

We use the Criterion~\cite{heisler_criterionrs_2023} benchmarking library to measure the performance of our engines and Miranda.
The original Miranda does not capture performance metrics, so we apply a small patch to the source code to output the time elapsed during a reduction operation.
The 20-line patch and instructions on how to apply it are included with the source code for our implementation.

Benchmarks were run on an otherwise quiescent laptop equipped with an x86-64 AMD CPU (Ryzen 7 4800U), running Debian 11 (Bullseye).
The original Miranda was compiled using GCC 10.2.1 without any optimization flags, to avoid breaking the garbage collector as discussed in Section~\ref{sec:miranda}.
All other code is written in Rust and compiled using the \texttt{release} profile (\texttt{rustc} version 1.65.0).

\subsection{Comparison with original Miranda}
Figure~\ref{fig:turner-vs-miranda} shows the performance of our Miranda-style engine with the traditional bracket abstraction compared to the original Miranda~\cite{turner_open_2021}.
